---
title: "TidyTuesday: The Office"
author: "Cosima Meyer"
date: "`r Sys.Date()`"
output: html_document
---

# Load all packages
```{r}
# clear workspace
rm(list = ls())

# install necessary packages
library(install.load)
packages <-
  c(
   "tidylog",
   "dplyr",
   "tidyr",
   "magrittr",
   "schrute",
   "ggplot2",
   "genderizeR",
   "tidytext",
   "ngram",
   "SnowballC",
   "quanteda",
   "spacyr",
   "forcats",
   "wesanderson"
   )

install_load(packages)

# Install via 
devtools::install_github("thebioengineer/tidytuesdayR")
library(tidytuesdayR)
```

# Load the data
```{r}
tuesdata <- tidytuesdayR::tt_load('2020-03-17')
tuesdata <- tidytuesdayR::tt_load(2020, week = 12)

# The Office ratings
office_ratings <- tuesdata$office_ratings
rm(tuesdata)

# Schrute data
schrute <- schrute::theoffice
```

Combine both datasets
```{r}
schrute$season <- as.numeric(schrute$season)
schrute$episode <- as.numeric(schrute$episode)

full_office <- left_join(schrute, office_ratings, by=c("season", "episode"))
```

# Preprocess text
```{r}
# Reduce the dataset
office_reduced <- full_office %>%
  select(text, writer, index, season, episode)

# Generate a corpus
mycorpus <-
  corpus(office_reduced,
         docid_field = "index",
         text_field = "text")

# tokenize
token <-
  tokens(
    mycorpus,
    remove_numbers = TRUE,
    remove_punct = TRUE,
    remove_symbols = TRUE,
    remove_twitter = TRUE,
    remove_url = TRUE,
    remove_hyphens = TRUE,
    include_docvars = TRUE
  )

token <- tokens_select(token,
                       min_nchar = 5)

# dfm
# define stopwords
mydfm <- dfm(token,
             tolower = TRUE,
             # stem = TRUE,
             remove = stopwords("english"))

# trim
mydfm.trim <-
  dfm_trim(
    mydfm,
    min_docfreq = 0.002,
    # min 2%
    max_docfreq = 0.90,
    #  max 90%
    docfreq_type = "prop"
  )
```

Convert the DFM to a data frame
```{r}
office_text <- convert(mydfm.trim, to = "data.frame")

# Gather (reshape)
office_gather <- office_text %>%
  gather(key = word, value = count, right:tail(colnames(office_text), 1))
```

Add and code some variables for the plot
```{r}
# generate count of episodes by writer
writer_count <- office_reduced %>%
  filter(
    writer == "Mindy Kaling" |
      writer == "Steve Carell" |
      writer == "Ricky Gervais;Stephen Merchant;Greg Daniels" |
      writer == "B.J. Novak"
  ) %>%
  count(season, episode, writer) %>%
  count(writer) %>%
  rename(episodes_by_writer = n)

# office_reduced %<>%
#   select(- c(season, episode))

# add writer
office_gather <- office_gather %>%
  mutate(index = as.numeric(document)) %>%
  left_join(office_reduced, by = "index") %>%
  left_join(writer_count, by = "writer")

# only keep rows if they arewriter
office_gather <- office_gather %>%
  filter(count != 0)


# get top words
plot_data <- office_gather %>%
  filter(
    writer == "Mindy Kaling" |
      writer == "Steve Carell" |
      writer == "Ricky Gervais;Stephen Merchant;Greg Daniels" |
      writer == "B.J. Novak"
  ) %>%
  #  group_by(season, episode, writer) %>%
  group_by(writer, word) %>%
  summarise(count_new = sum(count),
            episodes_by_writer = mean(episodes_by_writer))  %>%
  # standardize word count
  mutate(count_standardized = count_new / episodes_by_writer) %>%
  top_n(10, count_standardized) %>%
  mutate(highlight = ifelse(word == "michael", 1,
                            ifelse(
                              word == "dwight", 2,
                              ifelse(word == "birthday", 3, 0)
                            )))
```

# Plot: What are the favorite words of each writer?

Define colors for the plot (based on the `wesanderson` package)
```{r}
pal <- wes_palette(4, name = "Royal1", type = "discrete")
pal2 <- wes_palette(5, name = "Rushmore1", type = "continuous")
```

Plot for Mindy Kaling
```{r}
mindy <- plot_data %>%
  filter(writer == "Mindy Kaling") %>%
  ggplot() +
  geom_col(aes(
    x = count_standardized,
    y = reorder(factor(word), count_standardized),
    fill = factor(highlight)
  )) +
  theme_minimal() +
  scale_fill_manual(
    name = "",
    values = c(pal[1], pal[2], pal[4], pal2[3]),
    breaks = c(0, 1, 2, 3)
  ) +
  theme(
    title = element_text(size = 8, face = 'bold'),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +    xlim(0, 20) +
  labs(title = "Mindy Kaling",
       x = "Standardized word count", y = "")
```

Plot for Steve Carell
```{r}
steve <- plot_data %>% 
  filter(writer == "Steve Carell") %>% 
  ggplot() +
  geom_col(aes(x = count_standardized, y = reorder(factor(word), count_standardized), fill=factor(highlight))) +
  theme_minimal() +
 theme(
    title =element_text(size=8, face='bold'),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +  
  scale_fill_manual(
    name = "",
    values = c(pal[1], pal[2], pal[4], pal2[3]),
    breaks = c(0, 1, 2, 3)
  ) +
  xlim(0,20) +
  labs(title="Steve Carell",
        x ="", y = "")
```

Plot for Ricky Gervais, Stephen Merchant, and Greg Daniels
```{r}
crew <- plot_data %>%
  filter(writer == "Ricky Gervais;Stephen Merchant;Greg Daniels") %>%
  ggplot() +
  geom_col(aes(
    x = count_standardized,
    y = reorder(factor(word), count_standardized),
    fill = factor(highlight)
  )) +
  theme_minimal() +
  scale_fill_manual(
    name = "",
    values = c(pal[1], pal[2], pal[4], pal2[3]),
    breaks = c(0, 1, 2, 3)
  ) +
  theme(
    title = element_text(size = 8, face = 'bold'),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +    xlim(0, 20) +
  labs(title = "Ricky Gervais, Stephen Merchant, \nand Greg Daniels",
       x = "", y = "")
```

Plot for Benjamin Novak
```{r}
novak <- plot_data %>%
  filter(writer == "B.J. Novak") %>%
  ggplot() +
  geom_col(aes(
    x = count_standardized,
    y = reorder(factor(word), count_standardized),
    fill = factor(highlight)
  )) +
  theme_minimal() +
  scale_fill_manual(
    name = "",
    values = c(pal[1], pal[2], pal[4], pal2[3]),
    breaks = c(0, 1, 2, 3)
  ) +
  theme(
    title = element_text(size = 8, face = 'bold'),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  xlim(0, 20) +
  labs(title = "Benjamin Novak",
       x = "", y = "")
```


```{r}
# Bring all together
novak <- novak +
  theme(axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())

crew <- crew +
  theme(axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())

# Plot it together
plot1 <- (crew + novak + plot_layout(guides = "collect") &
    theme(legend.position = 'none')) 

plot2 <- (mindy + steve  + plot_layout(guides = "collect") & theme(legend.position = 'none'))

patchwork <- plot1 / plot2

plot <- patchwork + plot_annotation(
   title = "Every writer has a pet word...",
   caption = "#TidyTuesday: The Office\n Based on data from the schrute package\n Visualization: @cosima_meyer",
   theme = theme(
     plot.title = element_text(size = 15),
     plot.caption = element_text(size = 7)
   )
 )

ggsave(
  filename = "figures/TidyTuesday_Office.png",
  plot,
  width = 12,
  height = 9,
  dpi = 250,
  units = "in",
  device = 'png'
)
```

